\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-20 paper.qmd
Added MSE plot for choice of bins

>>>>

```{r}
training_data_scurve <- read_rds("data/s_curve/s_curve_training.rds")
```

<!--To generate errors for different total number of bins-->
```{r}
## To initialize number of bins along the x-axis
bin1_vec_scurve <- 2:27 #sqrt(NROW(training_data_scurve))

error_scurve <- data.frame(matrix(nrow = 0, ncol = 0))

for (xbins in bin1_vec_scurve) {

  bin2 <- calc_bins_y(bin1 = xbins, r2 = r2)$bin2

  scurve_model <- fit_highd_model(
    training_data = training_data_scurve,
    emb_df = umap_scurve_scaled,
    bin1 = xbins,
    r2 = r2,
    is_bin_centroid = TRUE,
    is_rm_lwd_hex = FALSE,
    col_start_highd = "x"
  )

  df_bin_centroids_scurve <- scurve_model$df_bin_centroids
  df_bin_scurve <- scurve_model$df_bin

  ## Compute error
  error_df <- glance(
    df_bin_centroids = df_bin_centroids_scurve,
    df_bin = df_bin_scurve,
    training_data = training_data_scurve,
    newdata = NULL,
    type_NLDR = "UMAP",
    col_start = "x") |>
    mutate(bin1 = xbins,
           bin2 = bin2,
           b = bin1 * bin2,
           b_non_empty = NROW(df_bin_centroids_scurve))

  error_scurve <- bind_rows(error_scurve, error_df)

}

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = 190, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  theme(axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, angle = 90))
```

```{r}
#| fig-cap: "MSE from UMAP applied to S-curve dataset with diffferent $b$ choices. What is the effective $b$ to create the model? The residual plot have a steep slope at the beginning, indicating that a smaller $b$ causes a larger amount of MSE. Then, the slope gradually declines or level off, indicating that a higher $b$ generates a smaller MSE. Using the elbow method, it was observed that when the $b$ is set to $190$, the lowest MSE occurred."
#| label: fig-mse-scurve-b
#| fig-pos: H
#| out-width: 50%

mse_scurve_b
```

### 2024-05-20 paper.tex
Added MSE plot for choice of bins

>>>>

\includegraphics[width=0.5\textwidth,height=\textheight]{paper_files/figure-pdf/fig-mse-scurve-b-1.pdf}

\caption{\label{fig-mse-scurve-b}MSE from UMAP applied to S-curve
dataset with diffferent \(b\) choices. What is the effective \(b\) to
create the model? The residual plot have a steep slope at the beginning,
indicating that a smaller \(b\) causes a larger amount of MSE. Then, the
slope gradually declines or level off, indicating that a higher \(b\)
generates a smaller MSE. Using the elbow method, it was observed that
when the \(b\) is set to \(190\), the lowest MSE occurred.}
